Sampling-Based Motion Planning for Tracking Evolution of Dynamic Tunnels in Molecular Dynamics Simulations

### 2017-10-31 paper.tex
image description from Adam

Many dynamic tunnels were discovered in the studied protein dynamics.
The inspection of the detected tunnels utilizes a simple visualization which shows all parts of the dynamic tunnel in one frame.
The example of this type of visualization is depicted in Fig.~\ref{fig::joint}.
Such visualization allows the biochemists to identify the surrounding residues and further study their physico-chemical properties and their influence on the tunnels.
For the analysis of a large simulation, an aggregation of the results is necessary.
In~\cite{fig::vis1}, the dynamic tunnels are visualized using vertical bars colored according to the number of frames occupied by this tunnel.

@@

{\textcolor{red}{TODO Fig.~\ref{fig::caver34}.}}

>>>>

Many dynamic tunnels were discovered in the studied protein dynamics.
The inspection of the detected tunnels utilizes a simple visualization which shows all parts of the dynamic tunnel in one frame.
The example of this type of visualization is depicted in Fig.~\ref{fig::joint}.
Such visualization allows the biochemists to identify the surrounding residues and further study their physico-chemical properties and their influence on the tunnels.
For the analysis of a large simulation, an aggregation of the results is necessary.
In Fig.~\ref{fig::vis1}, the dynamic tunnels are visualized using vertical bars colored according to the number of frames occupied by this tunnel.

@@

Furthermore, more detailed information about the tunnels detected in the simulation can be conveyed in an overview which depicts both static and dynamic tunnels in a row (Fig.~\ref{fig::caver34}).
This visualization shows whether there was a tunnel detected in a given snapshot and its type (static/dynamic).
The duration of a dynamic tunnel is depicted using colors.
This enables the user to see that there might exist multiple dynamic tunnels in a consecutive sequence of snapshots of the simulation.
